NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-12-18 RefereeReply1.txt

We would like to thank the referee for his/her constructive and valuable 
comments.  The points raised clearly helped us to further improve the 
quality of the manuscript.  Below we give detailed replies to the referee's 
queries and indicate the corresponding adjustments or additions to the 
manuscript.  We thereby follow the referee's initial ordering: 
1) The use of alpha(0) is motivated by the real emission that takes place at
   q^2=0. In order to obtain pole cancellation between the reals and the virtuals
   we chose the same factor for the virtual contribution. We are aware that there
   are other valid choices, however, at least in this case, the differences are small
   compared to the genuine electroweak corrections. We added a corresponding sentence
   about the motivation of the choice to the draft.
2) Renormalization- and factorization scale have been varied indepedently from 1/2 to 2 within 
   a 7 point scale variation, i.e. the combinations 0.5/2 and 2/0.5 are not present. The scale
   uncertainty has then be determined by the envelope of the various results.
   We added this information to the draft.
3) We added a sentence stating this explicitly.
4) The only analysis for three or more photons (Ref 6) focusses on heavy intermediate BSM
   particles. Therefore it did not make sense to adopt this set of cuts and we rather used generic
   cuts similar to the one applied for diphoton searches (i.e. asymmetric cuts between 1st and
   2nd photon). But they are not according to a specific experimental analysis. Nevertheless 
   they have been chosen in such a way that they are likely to be similar/comparable to a possible
   experimental analysis.
5)
6)
7)
8)  The figure captions have been corrected.
9)  This has been rephrased to clearly state which particles the invariant 
    mass cut acts on.
10) The PDFs have been specified, and the respective publication referenced.
11) Added reference to 1412.7421 and 1510.08742
12) The description of the observables has been enhanced in the following 
    cases:
    - Figure 6
    - Figures 8,11
13) We agree and added a sentence stating exactly that.

### 2017-12-21 RefereeReply1.txt

We would like to thank the referee for his/her constructive and valuable 
comments.  The points raised clearly helped us to further improve the 
quality of the manuscript.  Below we give detailed replies to the referee's 
queries and indicate the corresponding adjustments or additions to the 
manuscript.  We thereby follow the referee's initial ordering: 
1) The use of alpha(0) is motivated by the real emission that takes place at
   q^2=0. In order to obtain pole cancellation between the reals and the virtuals
   we chose the same factor for the virtual contribution. We are aware that there
   are other valid choices, however, at least in this case, the differences are small
   compared to the genuine electroweak corrections. We added a corresponding sentence
   about the motivation of the choice to the draft.
2) Renormalization- and factorization scale have been varied indepedently from 1/2 to 2 within 
   a 7 point scale variation, i.e. the combinations 0.5/2 and 2/0.5 are not present. The scale
   uncertainty has then be determined by the envelope of the various results.
   We added this information to the draft.
3) We added a sentence stating this explicitly.
4) The only analysis for three or more photons (Ref 6) focusses on heavy intermediate BSM
   particles. Therefore it did not make sense to adopt this set of cuts and we rather used generic
   cuts similar to the one applied for diphoton searches (i.e. asymmetric cuts between 1st and
   2nd photon). But they are not according to a specific experimental analysis. Nevertheless 
   they have been chosen in such a way that they are likely to be similar/comparable to a possible
   experimental analysis.
5) We have slightly improved the readability of the plots by adopting 
   dashed line styles for the jet vetoed NLO QCD prodictions and their 
   derivatives. The main focus, however, is on the ratio plots where 
   the lines lines are fewer and better to differentiate. The absolute 
   plot only serves to give the order of magnitude of the respective 
   cross sections.
6) The scales are determined by building an envelope around the 
   variation of the scaledependences detailed between eq. (3.2) and 
   (3.3). The ratio is then taken with respect to the central LO 
   prediction. "Hence, our NLO EW results exhibits the exact same 
   muF-dependence as the LO result", as is stated in the text directly 
   above eq. (3.3).
7) We have completed the sentence with mathematical relations of the sizes 
   of the QCD and EW corrections, it should be much clearer now.
8)  The figure captions have been corrected.
9)  This has been rephrased to clearly state which particles the invariant 
    mass cut acts on.
10) The PDFs have been specified, and the respective publication referenced.
11) Added reference to 1412.7421 and 1510.08742
12) The description of the observables has been enhanced in the following 
    cases:
    - Figure 6
    - Figures 8,11
13) We agree and added a sentence stating exactly that.

### 2017-12-22 RefereeReply1.txt

We would like to thank the referee for his/her constructive and valuable 
comments.  The points raised clearly helped us to further improve the 
quality of the manuscript.  Below we give detailed replies to the referee's 
queries and indicate the corresponding adjustments or additions to the 
manuscript.  We thereby follow the referee's initial ordering: 
1) The use of alpha(0) is motivated by the real emission that takes place at
   q^2=0. In order to obtain pole cancellation between the reals and the virtuals
   we chose the same factor for the virtual contribution. We are aware that there
   are other valid choices, however, at least in this case, the differences are small
   compared to the genuine electroweak corrections. We added a corresponding sentence
   about the motivation of the choice to the draft.
2) Renormalization- and factorization scale have been varied indepedently from 1/2 to 2 within 
   a 7 point scale variation, i.e. the combinations 0.5/2 and 2/0.5 are not present. The scale
   uncertainty has then be determined by the envelope of the various results.
   We added this information to the draft.
3) We added a sentence stating this explicitly.
4) The only analysis for three or more photons (Ref 6) focusses on heavy intermediate BSM
   particles. Therefore it did not make sense to adopt this set of cuts and we rather used generic
   cuts similar to the one applied for diphoton searches (i.e. asymmetric cuts between 1st and
   2nd photon). But they are not according to a specific experimental analysis. Nevertheless 
   they have been chosen in such a way that they are likely to be similar/comparable to a possible
   experimental analysis.
5) We have slightly improved the readability of the plots by adopting 
   dashed line styles for the jet vetoed NLO QCD prodictions and their 
   derivatives. The main focus, however, is on the ratio plots where 
   the lines lines are fewer and better to differentiate. The absolute 
   plot only serves to give the order of magnitude of the respective 
   cross sections.
6) The scales uncertainties are determined by building an envelope 
   around the variation of the scale dependences detailed between 
   eq. (3.2) and (3.3). The ratio is then taken with respect to the 
   central LO prediction. "Hence, our NLO EW results exhibits the 
   exact same muF-dependence as the LO result", as is stated in the 
   text directly above eq. (3.3). A sentence detailing this has also 
   been added to the caption of Fig. 4. In that sense, we do not 
   plot the electroweak correction as such, but the whole NLO EW 
   prediction, as the plot labels suggest.
7) We have completed the sentence with mathematical relations of the sizes 
   of the QCD and EW corrections, it should be much clearer now.
8)  The figure captions have been corrected.
9)  This has been rephrased to clearly state which particles the invariant 
    mass cut acts on.
10) The PDFs have been specified, and the respective publication referenced.
11) Added reference to 1412.7421 and 1510.08742
12) The description of the observables has been enhanced in the following 
    cases:
    - Figure 6
    - Figures 8,11
13) We agree and added a sentence stating exactly that.

### 2017-12-22 setup.tex
updated reference and reply

\Sherpa, on the other hand, provides the tree-level matrix 
elements, infrared subtraction, process management and phase-space 
integration of all contributions to all processes considered in 
this publication through its tree-level matrix element generator 
\textsc{Amegic} \cite{Krauss:2001iv}. 
Its inbuilt infrared subtraction is performed in the QED 
generalisation of the Catani-Seymour scheme~\cite{Catani:1996vz,
  Dittmaier:1999mb,Gleisberg:2007md,Kallweit:2014xda,
  Kallweit:2015dum,Kallweit:2017khh,Schonherr:2017xxx}
and includes the appropriate initial state mass factorisation 
counter terms.
Both programs, \Sherpa and \GoSam, are interfaced through a 
dedicated interface based on the 
Binoth Les Houches Accord~\cite{Binoth:2010xt,Alioli:2013nda}. 
Cross-checks of the tree-level matrix elements of \GoSam and 
\Sherpa and the renormalized pole coefficients of the virtual 
corrections of \GoSam and the infrared poles of \Sherpa have 
been performed for several phase space points spanning 
multiple kinematic regimes and we have found excellent 
agreement.

>>>>

\Sherpa, on the other hand, provides the tree-level matrix 
elements, infrared subtraction, process management and phase-space 
integration of all contributions to all processes considered in 
this publication through its tree-level matrix element generator 
\textsc{Amegic} \cite{Krauss:2001iv}. 
Its inbuilt infrared subtraction is performed in the QED 
generalisation of the Catani-Seymour scheme~\cite{Catani:1996vz,
  Dittmaier:1999mb,Gleisberg:2007md,Kallweit:2014xda,
  Kallweit:2015dum,Kallweit:2017khh,Schoenherr:2017xxx}
and includes the appropriate initial state mass factorisation 
counter terms.
Both programs, \Sherpa and \GoSam, are interfaced through a 
dedicated interface based on the 
Binoth Les Houches Accord~\cite{Binoth:2010xt,Alioli:2013nda}. 
Cross-checks of the tree-level matrix elements of \GoSam and 
\Sherpa and the renormalized pole coefficients of the virtual 
corrections of \GoSam and the infrared poles of \Sherpa have 
been performed for several phase space points spanning 
multiple kinematic regimes and we have found excellent 
agreement.
